\documentclass[a4paper,10pt]{article}

\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx, url, hyperref, palatino, tabularx, fontenc, inputenc, color, enumitem}
\definecolor{mygrey}{gray}{0.85}
\pagestyle{empty}

\newcommand{\resitem}[1]{\item #1}
\newcommand{\resheading}[1]{\vspace{0.5em} {\small \colorbox{mygrey}{{\begin{minipage}{0.975\textwidth}{{\textbf{#1}}}\end{minipage}}}} \vspace{0.5em}}
\newcommand{\ressubheading}[3]{\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r} \textbf{#1} & \textit{[#2]} \\ \end{tabular*}\vspace{-8pt}}

\begin{document}

\begin{center} \Large{\textbf{Ravi Prakash}} \end{center}

\vspace{2pt}

\begin{center} Software Development Engineer, Chennai, India - | Email: ravimehra1264@gmail.com | Phone: 9102904391 \end{center}
\begin{center} \href{linkedin.com/in/raviprakash1264}{linkedin.com/in/raviprakash1264} | \href{github.com/RaviPrakash1264}{github.com/RaviPrakash1264} \end{center}

\vspace{0.5em}
\resheading{Summary}
\resitem{A motivated individual with good knowledge of languages and development tools, seeking a position in a growth-oriented company where I can use my skills to the advantage of the company while having the scope to develop my own skills.}

\resheading{Education}
\ressubheading{B.TECH. COMPUTER SCIENCE AND ENGINEERING}{07/2018 - 06/2022}{VIT Univeristy, Vellore}
\resitem{CGPA: 8.45}

\resheading{Work Experience}
\ressubheading{Software Development Engineer}{08/2022 - Present}{Fiserv, Chennai}
\begin{itemize}[nosep]
    \resitem{Working with merchant portal team to scale the businesses of merchants in EMEA region.}
    \resitem{Implemented and integrated JWT Authentication and role-based authorization using Spring Security.}
    \resitem{Integrated third-party APIs and services for chatbot feature.}
    \resitem{Utilized caching mechanisms and lazy initialization to implement RESTful APIs which has led to decrement of response time by more than 60\%.}
    \resitem{Used Swagger UI to interact and visualize different REST APIs endpoints.}
\end{itemize}
\ressubheading{Honeywell Accelerator Program}{08/2020 - 12/2020}{Honeywell, Remote}
\begin{itemize}[nosep]
    \resitem{Worked on a real-time project which was mentored by honeywell developers.}
    \resitem{Made a Usage Tracking website for a single-page web app using Spring boot, Hibernate, HTML, CSS, Bootstrap and Angular.}
\end{itemize}
\ressubheading{Full Stack Developer Intern}{03/2020 - 05/2020}{Foxmula, Remote}
\begin{itemize}[nosep]
    \resitem{Learned various skills in web development domain implementing Spring boot, Hibernate and Thymeleaf.}
    \resitem{Made clone of a website named Livspace.}
\end{itemize}

\resheading{Certificates}
\resitem{Spring and Spring Boot Masterclass}
\resitem{Full Stack Web Development Masterclass: Beginner to Advanced}
\resitem{DSA Self Paced}

\resheading{Skills}
\resitem{Java, Spring Boot, Hibernate, Thymeleaf, HTML, CSS, Bootstrap, JavaScript, TypeScript, C++, Angular, MySQL, PostgreSQL, Swagger}

\resheading{Personal Projects}
\ressubheading{Let's Blog}{}{}
\resitem{A complete backend solution for a blogging application which provides numerous functionalities to the frontend developers. It helps users to create, delete, update, sort, search, categorize a post according to a particular category and used Pagination to show the list of posts in different pages to save resources. Implemented JWT authentication and role-based authorization to secure and manage the access of APIs and used lazy initialization to improve the performance of the app. Implemented user input validation and global exception handling to make the application robust towards unwanted interruptions. Implemented advanced hibernate mappings to establish the relationship between different database tables and used Swagger UI to document the APIs.}
\ressubheading{PingMe}{}{}
\resitem{A All in One solution for managing your servers whether it be a broadband or router or your personal computer. It will consist of multiple functionalities which includes add, delete, custom form validation, filter servers on basis of their status, notification service and pinging the servers. It will help users to generate the report of the servers in excel format and it also have multi-device adaptability.}
\ressubheading{Employee Manager}{}{}
\resitem{A one stop solution for employee management. Unlike any other webapps, it provides add, delete, update, filter/search of any set of employees along with the alert prompt and have multi-device adaptability.}

\resheading{Coding Handles}
\resitem{CodeChef: 4 Star}
\resitem{Leetcode: Top 25\%}
\resitem{GeeksforGeeks: 550+ Problems Solved}


\end{document}