\documentclass[a4paper,10pt]{article}

\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx, url, hyperref, palatino, tabularx, fontenc, inputenc, color, enumitem}
\definecolor{mygrey}{gray}{0.85}
\pagestyle{empty}

\newcommand{\resitem}[1]{\item #1}
\newcommand{\resheading}[1]{\vspace{0.5em} {\small \colorbox{mygrey}{{\begin{minipage}{0.975\textwidth}{{\textbf{#1}}}\end{minipage}}}} \vspace{0.5em}}
\newcommand{\ressubheading}[3]{\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r} \textbf{#1} & \textit{[#2]} \\ \end{tabular*}\vspace{-8pt}}

\begin{document}

\begin{center} \Large{\textbf{Ravi Prakash}} \end{center}

\vspace{2pt}

\begin{center} Software Development Engineer, Chennai, India - | Email: ravimehra1264@gmail.com | Phone: 9102904391 \end{center}
\begin{center} \href{linkedin.com/in/raviprakash1264}{linkedin.com/in/raviprakash1264} | \href{github.com/RaviPrakash1264}{github.com/RaviPrakash1264} \end{center}

\resheading{Summary}
\resitem{A motivated individual with good knowledge of languages and development tools, seeking a position in a growth-oriented company where I can use my skills to the advantage of the company while having the scope to develop my own skills.}

\resheading{Education}
\ressubheading{B.TECH. COMPUTER SCIENCE AND ENGINEERING}{VIT University, Vellore}{07/2018 - 06/2022, 8.45}

\resheading{Work Experience}
\ressubheading{Software Development Engineer}{Fiserv, Chennai}{08/2022 - Present}
\begin{itemize}[noitemsep]
    \resitem{Working with merchant portal team to scale the businesses of merchants in EMEA region.}
    \resitem{Implemented and integrated JWT Authentication and role-based authorization using Spring Security.}
    \resitem{Integrated third-party APIs and services for chatbot feature.}
    \resitem{Utilized caching mechanisms and lazy initialization to implement RESTful APIs which has led to decrement of response time by more than 60\%.}
    \resitem{Used Swagger UI to interact and visualize different REST APIs endpoints.}
\end{itemize}
\ressubheading{Honeywell Accelerator Program}{Honeywell (Remote)}{08/2020 - 12/2020}
\begin{itemize}[noitemsep]
    \resitem{Worked on a real-time project which was mentored by Honeywell developers.}
    \resitem{Made a Usage Tracking website for a single-page web app using Spring boot, Hibernate, HTML, CSS, Bootstrap and Angular.}
\end{itemize}
\ressubheading{Full Stack Developer Intern}{Foxmula (Remote)}{03/2020 - 05/2020}
\begin{itemize}[noitemsep]
    \resitem{Learned various skills in web development domain implementing Spring boot, Hibernate and Thymeleaf.}
    \resitem{Made clone of a website named Livspace.}
\end{itemize}

\resheading{Certificates}
\begin{itemize}[noitemsep]
    \resitem{Spring and Spring Boot Masterclass}
    \resitem{Full Stack Web Development Masterclass: Beginner to Advanced}
    \resitem{DSA Self Paced}
\end{itemize}

\resheading{Skills}
\resitem{Java, Spring Boot, Hibernate, Thymeleaf, HTML, CSS, Bootstrap, JavaScript, TypeScript, C++, Angular, MySQL, PostgreSQL, Swagger}

\resheading{Personal Projects}
\ressubheading{Let's Blog}{}{}
\begin{itemize}[noitemsep]
    \resitem{A complete backend solution for a blogging application which provides numerous functionalities to the frontend developers.}
    \resitem{It helps users to create, delete, update, sort, search, categorize a post according to a particular category and used Pagination to show the list of posts in different pages to save resources.}
    \resitem{Implemented JWT authentication and role-based authorization to secure and manage the access of APIs and used lazy initialization to improve the performance of the app.}
    \resitem{Implemented user input validation and global exception handling to make the application robust towards unwanted interruptions.}
    \resitem{Implemented advanced hibernate mappings to establish the relationship between different database tables and used Swagger UI to document the APIs.}
\end{itemize}
\ressubheading{PingMe}{}{}
\begin{itemize}[noitemsep]
    \resitem{An All in One solution for managing your servers whether it be a broadband or router or your personal computer.}
    \resitem{It will consist of multiple functionalities which includes add, delete, custom form validation, filter servers on basis of their status, notification service and pinging the servers.}
    \resitem{It will help users to generate the report of the servers in excel format and it also have multi-device adaptability.}
\end{itemize}
\ressubheading{Employee Manager}{}{}
\begin{itemize}[noitemsep]
    \resitem{A one stop solution for employee management.}
    \resitem{Unlike any other webapps, it provides add, delete, update, filter/search of any set of employees along with the alert prompt and have multi-device adaptability.}
\end{itemize}

\resheading{Coding Handles}
\resitem{CodeChef: 4 Star}
\resitem{Leetcode: Top 25\%}
\resitem{GeeksforGeeks: 550+ Problems Solved}


\end{document}