\documentclass[a4paper,10pt]{article}

\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx, url, hyperref, palatino, tabularx, fontenc, inputenc, color, enumitem}
\definecolor{mygrey}{gray}{0.85}
\pagestyle{empty}

\newcommand{\resitem}[1]{\item #1}
\newcommand{\resheading}[1]{\vspace{0.5em} {\small \colorbox{mygrey}{{\begin{minipage}{0.975\textwidth}{{\textbf{#1}}}\end{minipage}}}\vspace{0.5em}}
\newcommand{\ressubheading}[3]{\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r} \textbf{#1} & \textit{[#2]} \\ \end{tabular*}\vspace{-8pt}}

\begin{document}

\begin{center} \Large{\textbf{ANJALIKUMARI}} \end{center}

\vspace{2pt}

\begin{center} \small{anjalikumari625213@gmail.com}, \small{linkedin.com/in/anjali-kumari6252}, \small{+91-9708320363} \end{center}

\resheading{Professional Profile}
\begin{itemize}[nosep]
    \resitem{AWS Certified Cloud Practitioner; Developer Associate}
    \resitem{5+ years of experience as a Software Engineer in the IT industry.}
    \resitem{2017 Graduate (Computer Science Engineering) from Birla Institute of Technology, Mesra}
    \resitem{Experience in domains such as Banking, Finance and Insurance, Telecom.}
    \resitem{Have good understanding of Data Structures, Algorithms, Programming Concepts and Problem-Solving Skills}
\end{itemize}

\resheading{Technical Skills}
\begin{itemize}[nosep]
    \resitem{Languages/Technologies: Java, Springboot, Hibernate, Python}
    \resitem{Testing Tools: Junit, TestNG, Mockito, Postman, Swagger UI,}
    \resitem{Database: Postgres, MongoDB}
    \resitem{Version Control/Build Tools: Bitbucket, GIT, Maven, Jenkins}
    \resitem{Containerization Tools: Red Hat OpenShift Container, Docker}
    \resitem{Platforms/Software Packages: Intellij, Eclipse, Visual Studio}
    \resitem{Defect Management Tools: JIRA, Rally, Zephyr}
    \resitem{Cloud Computing: AWS CloudFormation, API Gateway, Amazon SQS, AWS Identity and Access Management, AWS CloudWatch}
\end{itemize}

\resheading{Work Experience}
\ressubheading{Capgemini, Pune}{Aug 2021 - Present}{Senior Consultant}
\begin{itemize}[nosep]
    \resitem{GERenewables:}
    \resitem{\hspace{0.5cm}Developed Web applications using Java, Springboot and Hibernate based RESTful services.}
    \resitem{\hspace{0.5cm}Worked on Project Migration from On-Premise to AWS cloud Serverless architecture.}
    \resitem{\hspace{0.5cm}Worked on Kubernetes and Jenkins for automated deployment and management of containerized application}
    \resitem{\hspace{0.5cm}Integrated project with monitoring tools like Kibana and New Relic to handle high volume of request.}
    \resitem{\hspace{0.5cm}Integrated MongoDB queries to migrate the application from PostgreSQL.}
    \resitem{\hspace{0.5cm}Designed AWS CloudFormation template to provision stacks for APIs in API Gateway.}
\end{itemize}
\textit{Technology/Platform: Java, Springboot, GIT, AWS CloudFormation, API Gateway, MongoDB, Jenkins, Kubernetes, Kibana}

\ressubheading{Amdocs, Pune}{June 2020 – July 2021}{Software Engineer}
\begin{itemize}[nosep]
    \resitem{1. Globe:}
    \resitem{\hspace{0.5cm}To handle the product order request from the customer such as add, cancel, change or terminate in the telecom domain.}
    \resitem{\hspace{0.5cm}Responsibilities:}
    \resitem{\hspace{1cm}Coordinated with developers in designing and developing Microservices REST APIs for order handling process using Spring and Hibernate.}
    \resitem{\hspace{1cm}Created End to End Automation script for order handling flow using RestAssured, JACKSON and other libraries.}
    \resitem{\hspace{1cm}Having experience in configuring Red Hat OpenShift Container for web service URL and tracking the logs.}
    \resitem{\hspace{1cm}Automated E2E functionality from backend database to Rest api through SQL Server and Implemented CI/CD for the project through Jenkins.}
    \resitem{\hspace{1cm}Act within a cross-functional, scrum-based team focused on agile and continuous software delivery}
\end{itemize}
\textit{Technology/Platform: Springboot, Hibernate, Java, J2EE, Jenkins, OCP, Junit, Maven, SQL Server.}


\ressubheading{Infosys Ltd, Pune}{Jan 2018 – June 2020}{System Engineer}
\begin{itemize}[nosep]
    \resitem{1. Bank technology:}
    \resitem{\hspace{0.5cm}Web Services to get the details of Customer and its associated debit card, credit card, travel itineraries etc and maintenance of their card when lost, damaged or stolen in the Banking domain.}
    \resitem{\hspace{0.5cm}Responsibilities:}
    \resitem{\hspace{1cm}Have good exposure of Web Services in Rest API to verify the features of services by defining headers, payload, Data format (JSON, XML) and other resources using ParaSoft SOA tool.}
    \resitem{\hspace{1cm}Having experience in configuring and integrating Automated scripts on CI/CD tools like GIT, Bitbucket, Jenkins.}
    \resitem{\hspace{1cm}Experience in API testing to satisfy the business logic and requirements using Swagger UI and Postman.}
    \resitem{\hspace{1cm}Deployed artifacts on PCF or VM box using Linux commands and verified ELI logs on Splunk.}
    \resitem{\hspace{1cm}Involved in writing and executing SQL queries to validate the backend data.}
\end{itemize}
\textit{Technology/Platform: Java, Parasoft SOA tool, Postman, Swagger UI, RestAssured, Selenium Webdriver, BDD Framework, Maven, TestNG, Junit, Bamboo, Bitbucket, GIT.}

\resheading{Certifications}
\begin{itemize}[nosep]
    \resitem{AWS Certified Associate Developer}
    \resitem{Infosys Certified Agile developer}
    \resitem{Infosys Certified Java SE 8}
    \resitem{Infosys Certified DevOps Professional}
\end{itemize}

\resheading{Achievements}
\begin{itemize}[nosep]
    \resitem{Certificate of participation in IT Olympiad 2016 presented by COMPUTER SOCIETY OF INDIA (PUNE CHAPTER) \& ROTARY CLUB OF PUNE PRIDE.}
    \resitem{Certificate of participation in State Level of innovation in science pursuit for Inspired Research (22-24th March 2012).}
    \resitem{Second runner up in District Level Science Exhibition Under INSPIRE AWARD SCHEME for learning of science (30-31st Jan 2012).}
    \resitem{Certification of Web development Team Member in Aurora’16 (University Literary Fest)}
\end{itemize}

\resheading{Educational Qualification}
\begin{itemize}[nosep]
    \resitem{Bachelor of Engineering (BE) in Computer Science Engineering (2017) \\ Birla Institute of Technology, Mesra [CGPA-7.63 with Distinction]}
    \resitem{Senior Secondary, XIIth (2013) \\ State Board [Percentage–74.8\%]}
    \resitem{Secondary, Xth (2011) \\ State Board [Percentage–83.2\%]}
\end{itemize}

\end{document}